method

### 2022-06-08 06_Paper/ER-ED/method.Rmd
corrected typo

Further psychological constructs will be assessed but have no clear hypothesies in the present work an are therefore investigated only exploratory:
General psychological well-being will be assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] will be used.
Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job[@Bernecker2017].
To assess Need for Cognition, the German version short form of the Need for Cognition Scale[@Cacioppo1982; @Bless1994] will be used.
To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)[@Schwarzer1999], the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011].
Attentional control will be assessed using the Attentional Control Scale (ACS)[@Derryberry2002].
For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).

>>>>

Further psychological constructs will be assessed but have no clear hypotheses in the present work and are therefore investigated only exploratory:
General psychological well-being will be assessed using the German version of the WHO-5 scale[@Bech2004; @Braehler2007].
To measure resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] will be used.
Habitual use of ER will be assessed using the German version of the Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003; @Abler2009].
Implicit theories of willpower in emotion control will be assessed using the implicit theories questionnaire from Bernecker and Job[@Bernecker2017].
To assess Need for Cognition, the German version short form of the Need for Cognition Scale[@Cacioppo1982; @Bless1994] will be used.
To assess self-control [@Paschke2016], sum scores of the German versions of the following questionnaires will be used: the Self-Regulation Scale (SRS)[@Schwarzer1999], the Brief Self-Control Scale (BSCS)[@Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011].
Attentional control will be assessed using the Attentional Control Scale (ACS)[@Derryberry2002].
For more detailed information on psychometric properties of the questionnaires, please see [supplementary material](#SupplementQuestionnaires).
